A Standard for the Scholarly Citation of Archaeological Data: Supplementary Information

### 2017-08-26 analysis/paper/paper.Rmd
stash

---
title: "A Standard for the Scholarly Citation of Archaeological Data: Supplementary Information"
author:
  - "Ben Marwick"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
bibliography: references.bib
csl: journal-of-archaeological-science.csl
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

The source file for this document, and other files in the compendium are online at https://github.com/benmarwick/datacitation

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

>>>>

---
title: "A Standard for the Scholarly Citation of Archaeological Data: Supplementary Information"
author:
  - "Ben Marwick"
  - "Suzanne E. Pilaar Birch"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
bibliography: references.bib
csl: journal-of-archaeological-science.csl
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored.

@@

The source file for this document, and other files in the compendium are online at https://github.com/benmarwick/datacitation
-->
